Output Summary

### 2023-08-18 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Improve the noise term diagnostics Rmd section

# Random Noise Diagnostics {.tabset .tabset-pills}

@@

This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
Diagnostics are separate by process model and observation model and the time series of noise terms is displayed to visually detect issues.
Each model component (process or observation) includes summary tables that quantitatively summarize the results displayed on the time series figures.

#### Why Does this Matter?

@@

#### What was Calculated?

@@

##### JAGS Code Example

@@

<details>
<summary>Click to Show Example Code</summary>
<pre>
# priors
mu_phi ~ dbeta(1,1)
sigma_Lphi ~ dunif(0,5)
&nbsp;
for (y in 1:ny) {
  # random process
  Lphi[y] ~ dnorm(logit(mu_phi), 1/sigma_Lphi^2)
  phi[y] &lt;- ilogit(Lphi[y])
  &nbsp;
  # standardized process noise term
  phi_qresid[y] &lt;- pnorm(logit(phi[y]), logit(mu_phi), 1/sigma_Lphi^2)
  &nbsp;
  # likelihood statement for fitting model
  x_surv[y] ~ dbin(phi[y], n_tagged[y])
  &nbsp;
  # standardized observation noise term
  x_surv_qresid[y] <- pbin(x_surv[y], phi[y], n_tagged[y])
} </pre>
</details>

#### What is Shown?

@@

## Process Model Noise Terms {.tabset .tabset-pills}

@@

### FW Juvenile {.tabset .tabset-pills}

@@

```{r egg-to-parr-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Egg \u2192 Parr Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pi-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,LH_type,pop]", pop = j, main = pops[j], LH_type = i_fall))
axis_labels("Brood Year", "logit(Proportion Fall Migrants) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

##### Fall Migrants

```{r overwinter-surv-noise-fall, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
axis_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### Spring Migrants

```{r overwinter-surv-noise-spring, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r growth-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Parr \u2192 Smolt 'Growth' Factor) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Trib $\to$ LGR {.tabset .tabset-pills}

##### NOR

```{r trib-to-LGR-surv-nor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 1, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [NOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r trib-to-LGR-surv-hor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 2, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [HOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r LGR-to-BON-surv-noise, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

### SW Juvenile {.tabset .tabset-pills}

@@

```{r yr1-ocean-surv-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Yr1 Ocean Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

##### NOR

```{r pr-mat-3-nor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-3 [NOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r pr-mat-3-hor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-3 [HOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

##### NOR

```{r pr-mat-4-nor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-4 [NOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r pr-mat-4-hor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-4 [HOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

### FW Adult {.tabset .tabset-pills}

@@

```{r BON-to-LGR-surv-noise, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Return Year", "logit(BON \u2192 LGR Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

## Observation Model Noise Terms {.tabset .tabset-pills}

@@

### Abundance Data {.tabset .tabset-pills}

@@

```{r fall-trap-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Fall Parr Abundance) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-trap-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Spring Trap Count) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r adult-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Return Year", "log(Total Adult Count) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

### Survival Data {.tabset .tabset-pills}

@@

```{r summer-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Summer Parr \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r fall-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Fall Parr \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r winter-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
  }
})
axis_labels("Brood Year", "logit(Winter Parr \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

##### NOR

```{r spring-surv-resid-nor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
axis_labels("Brood Year", "logit(NOR Smolt \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r spring-surv-resid-hor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
  }
})
axis_labels("Brood Year", "logit(HOR Smolt \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r hydro-surv-resid, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

### Length Data {.tabset .tabset-pills}

@@

```{r summer-length-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Parr Mean Length) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-length-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Smolt Mean Length) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

### Composition Data {.tabset .tabset-pills}

@@

##### CAT

@@

##### LOS

@@

##### MIN

@@

##### UGR

@@

#### Carcass Sampling {.tabset .tabset-pills}

>>>>

# Residual Diagnostics {.tabset .tabset-pills}

@@

This section is devoted to evaluating how consistent the estimated process and observation noise terms (i.e., residuals) are with the assumptions of the random processes they are assumed to be generated by.
Diagnostics are separated by process model and observation model and the time series of noise terms is displayed to visually detect issues.
Each model component (process or observation) includes summary tables that summarize the results displayed on the time series figures.

#### Why Does this Matter? {-}

@@

#### What was Calculated? {-}

@@

##### JAGS Code Example {-}

@@

<details>
<summary>Click to Show Example Code</summary>
<pre>
# priors
mu_phi ~ dbeta(1,1)
sigma_Lphi ~ dunif(0,2)
&nbsp;
for (y in 1:ny) {
  # random process
  Lphi[y] ~ dnorm(logit(mu_phi), 1/sigma_Lphi^2)
  phi[y] &lt;- ilogit(Lphi[y])
  &nbsp;
  # standardized process noise term
  phi_qresid[y] &lt;- pnorm(logit(phi[y]), logit(mu_phi), 1/sigma_Lphi^2)
  &nbsp;
  # likelihood statement for fitting model
  x_surv[y] ~ dbin(phi[y], n_tagged[y])
  &nbsp;
  # standardized observation noise term
  x_surv_qresid[y] <- pbin(x_surv[y], phi[y], n_tagged[y])
} </pre>
</details>

#### What is Shown? {-}

@@

## Process Model Noise Terms {.tabset .tabset-dropdown}

@@

### FW Juvenile {.tabset .tabset-dropdown}

@@

```{r egg-to-parr-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "Egg \u2192 Parr Survival QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pi-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,LH_type,pop]", pop = j, main = pops[j], LH_type = i_fall))
axis_labels("Brood Year", "Proportion Fall Migrants QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

##### Fall Migrants {-}

```{r overwinter-surv-noise-fall, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
axis_labels("Brood Year", "Over-winter Survival (Fall Migrants) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### Spring Migrants {-}

```{r overwinter-surv-noise-spring, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "Over-winter Survival (Spring Migrants) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r growth-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "Parr \u2192 Smolt 'Growth' Factor QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Smolt $\to$ LGR {.tabset .tabset-pills}

##### NOR {-}

```{r trib-to-LGR-surv-nor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 1, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR {-}

```{r trib-to-LGR-surv-hor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 2, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "Smolt \u2192 LGR Survival (HOR) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r LGR-to-BON-surv-noise, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Brood Year", "LGR \u2192 BON Survival QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

### SW Juvenile {.tabset .tabset-dropdown}

@@

```{r yr1-ocean-surv-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "Yr1 Ocean Survival QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

##### NOR {-}

```{r pr-mat-3-nor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "Pr(Mature at Age-3|NOR) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR {-}

```{r pr-mat-3-hor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
axis_labels("Brood Year", "Pr(Mature at Age-3|HOR) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

##### NOR {-}

```{r pr-mat-4-nor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "Pr(Mature at Age-4|NOR) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR {-}

```{r pr-mat-4-hor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
axis_labels("Brood Year", "Pr(Mature at Age-4|HOR) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

### FW Adult {.tabset .tabset-dropdown}

@@

```{r BON-to-LGR-surv-noise, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Return Year", "BON \u2192 LGR Survival QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

## Observation Model Noise Terms {.tabset .tabset-dropdown}

@@

### Abundance Data {.tabset .tabset-dropdown}

@@

```{r fall-trap-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "Fall Parr Abundance QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-trap-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "Spring Smolt Abundance QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r adult-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Return Year", "Total Adult Return QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

### Survival Data {.tabset .tabset-dropdown}

@@

```{r summer-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "Summer Parr \u2192 LGR Survival QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r fall-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "Fall Parr \u2192 LGR Survival QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r winter-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
  }
})
axis_labels("Brood Year", "Winter Parr \u2192 LGR Survival QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

##### NOR {-}

```{r spring-surv-resid-nor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

##### HOR {-}

```{r spring-surv-resid-hor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
  }
})
axis_labels("Brood Year", "Smolt \u2192 LGR (NOR) Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r hydro-surv-resid, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Brood Year", "LGR \u2192 BON Survival QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

### Length Data {.tabset .tabset-dropdown}

@@

```{r summer-length-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "Parr Mean Length QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-length-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "Smolt Mean Length QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

### Composition Data {.tabset .tabset-dropdown}

@@

##### CAT {-}

@@

##### LOS {-}

@@

##### MIN {-}

@@

##### UGR {-}

@@

#### Carcass Sampling {.tabset .tabset-dropdown}
